A Bidirected String Graph Model of Genome Assembly

### 2012-12-04 presentation/presentation.tex
Modify read overlaps

		\begin{tikzpicture}[>=\ReadArrowType]
				\draw[<-,style=very thick] (0.0, 0.0) -- (4.0, 0.0);
				\draw[->,style=very thick] (1.2, -0.3) -- (5.2, -0.3);
				\draw[<-,style=very thick] (2.4, -0.6) -- (6.4, -0.6);
				\draw[<-,style=very thick] (3.6, -0.9) -- (7.6, -0.9);
				\draw (-0.3, 0.0) node {1.};
				\draw (-0.3, -0.3) node {2.};
				\draw (-0.3, -0.6) node {3.};
				\draw (-0.3, -0.9) node {4.};
		\end{tikzpicture}
		\caption{A bidirected graph and the implied assembly of the
		corresponding reads}
	\end{figure}
\end{frame}

@@

\begin{frame}{Arrival rate statistic (A-statistic)}
	\begin{itemize}
		\item The {\bf A-statistic} $A(e)$ of an edge $e$ in a
		bidirected string graph is:
	\end{itemize}
	\[ A(e) = \frac{n}{G} \Delta - \log_2{k} \]
	where $n$ is the total number of reads, $G$ is the estimated genome
	length, $\Delta$ is the length of the edge in bp, and $k$ is the number
	of reads that support that edge.
	\begin{itemize}
		\item The A-statistic is the logarithm of the probability that
		an edge represents unique sequence rather than duplicate
		sequence.
	\end{itemize}
\end{frame}

\begin{frame}{Implementation}
	\begin{minipage}{0.3\textwidth}
		\begin{itemize}
			\item A set of C++ programs that iteratively transform the data into
			the final assembly.
			\item Yellow programs are not yet implemented.
		\end{itemize}
	\end{minipage}
	\begin{minipage}{0.67\textwidth}
		\includegraphics[width=1.0\textwidth]{programs.pdf}
	\end{minipage}
\end{frame}

>>>>

		\begin{tikzpicture}[>=\ReadArrowType]
				\draw[<-,style=very thick] (0.0, 0.0) -- (2.6, 0.0);
				\draw[->,style=very thick] (1.6, -0.3) -- (4.2, -0.3);
				\draw[<-,style=very thick] (3.2, -0.6) -- (5.8, -0.6);
				\draw[<-,style=very thick] (4.8, -0.9) -- (7.4, -0.9);
				\draw (-0.3, 0.0) node {1.};
				\draw (-0.3, -0.3) node {2.};
				\draw (-0.3, -0.6) node {3.};
				\draw (-0.3, -0.9) node {4.};
		\end{tikzpicture}
		\caption{A bidirected graph and the implied assembly of the
		corresponding reads}
	\end{figure}
\end{frame}

@@

\begin{frame}{Arrival rate statistic (A-statistic)}
	\begin{itemize}
		\item The {\bf A-statistic} $A(e)$ of an edge $e$ in a
		bidirected string graph is:
	\end{itemize}
	\[ A(e) = \frac{n}{G} \Delta - \ln{2} \cdot {k} \]
	where $n$ is the total number of reads, $G$ is the estimated genome
	length, $\Delta$ is the length of the edge in bp, and $k$ is the number
	of reads that support that edge.
	\begin{itemize}
		\item The A-statistic is the logarithm of the probability that
		an edge represents unique sequence rather than duplicate
		sequence.
	\end{itemize}
\end{frame}

\begin{frame}{Implementation}
	\begin{minipage}{0.3\textwidth}
		\begin{itemize}
			\item A set of C++ programs that iteratively transform
			the data on-disk into the final assembly.
			\item Yellow programs are not yet implemented.
		\end{itemize}
	\end{minipage}
	\begin{minipage}{0.67\textwidth}
		\includegraphics[width=1.0\textwidth]{programs.pdf}
	\end{minipage}
\end{frame}
